### 2025-07-01 index.qmd
20250701 - visualizing regression results

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "downlit", "xml2",
  "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", "gsisdecoder", 
  "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", "dagitty", 
  "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", "patchwork", 
  "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", 
  "AICcmodavg", "rstan", "brms", "bbmle", "fitdistrplus", "mclust", "magrittr", 
  "viridis", "plotly", "quantmod", "fPortfolio", "xts", "zoo", "forecast", #"webshot2", 
  "stringi", "parallel", "parallelly", "doParallel", "missRanger", "ggridges", 
  "powerjoin", "caret", "gpboost", "cmdstanr", "learnr", "remotes", "corrplot", 
  "correlation", "mgcv", "rms", "car", "performance", "lavaan", "mice", 
  "miceadds", "interactions", "shiny", "PearsonDS", "robustbase", "data.table", 
  "future", "future.apply", "SimDesign"
)

>>>>

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "broom", "downlit", 
  "xml2", "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", 
  "patchwork", "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", 
  "sjstats", "AICcmodavg", "rstan", "brms", "bbmle", "fitdistrplus", "sn", 
  "mclust", "magrittr", "viridis", "plotly", "quantmod", "fPortfolio", "NMOF", 
  "xts", "zoo", "forecast", "stringi", "parallel", "parallelly", "doParallel", #"webshot2"
  "missRanger", "ggridges", "powerjoin", "caret", "gpboost", "cmdstanr", "learnr", 
  "remotes", "corrplot", "correlation", "mgcv", "rms", "car", "performance", 
  "lavaan", "mice", "miceadds", "interactions", "shiny", "PearsonDS", 
  "robustbase", "data.table", "future", "future.apply", "QuantPsyc", "SimDesign"
)

### 2025-07-01 multiple-regression.qmd
20250701 - visualizing regression results

```{r}
library("petersenlab")
library("rms")
library("car")
library("caret")
library("lme4")
library("performance")
library("lavaan")
library("mice")
library("miceadds")
library("interactions")
library("brms")
library("robustbase")
library("tidyverse")
library("knitr")
```

@@

If we want to obtain standardized regression coefficients, we can standardize the [outcome variable](#sec-correlationalStudy) and each [predictor variable](#sec-correlationalStudy) using the `scale()` function:

@@

Only the quadratic term for target share shows a significant association.
If we wanted to visualize the shape of the model-implied association between target share and fantasy points, we could generate the model-implied predictions using the data range that we want to visualize.

>>>>

```{r}
library("petersenlab")
library("rms")
library("car")
library("caret")
library("lme4")
library("performance")
library("lavaan")
library("mice")
library("miceadds")
library("interactions")
library("brms")
library("robustbase")
library("QuantPsyc")
library("broom")
library("tidyverse")
library("knitr")
```

@@

If we want to obtain standardized regression coefficients, we can use the `lm.beta()` function of the `QuantPsyc` package.

```{r}
QuantPsyc::lm.beta(linearRegressionModel)
```

Or, we can standardize the [outcome variable](#sec-correlationalStudy) and each [predictor variable](#sec-correlationalStudy) using the `scale()` function:

@@

Only the quadratic term for target share (not height or weight) shows a significant association.

Here are the standardized coefficients:

```{r}
QuantPsyc::lm.beta(quadraticTermsRegressionModel)
```

```{r}
quadraticTermsRegressionModelStandardized <- lm(
  scale(fantasyPoints) ~ scale(age) + scale(I(age^2)) + scale(height) + scale(I(height^2)) + scale(weight) + scale(I(weight^2)) + scale(target_share) + scale(I(target_share^2)),
  data = player_stats_seasonal %>% filter(position %in% c("WR")),
  na.action = "na.exclude"
)

summary(quadraticTermsRegressionModelStandardized)
```

### Visualizing Regression Results {#sec-multipleRegressionVisualizingResults}

#### Regression Coefficients {#sec-multipleRegressionVisualizingRegressionCoefficients}

To visualize the regression coefficients, we can use the `tidy()` function of the `broom` package.

```{r}
quadraticTermsRegressionModel_tidy <- tidy(
  quadraticTermsRegressionModel,
  conf.int = TRUE)

quadraticTermsRegressionModelStandardized_tidy <- tidy(
  quadraticTermsRegressionModelStandardized,
  conf.int = TRUE)
```

```{r}
#| label: fig-regressionCoefficients
#| fig-cap: "Regression Coefficients with 95% Confidence Interval."
#| fig-alt: "Regression Coefficients with 95% Confidence Interval."

ggplot(
  quadraticTermsRegressionModel_tidy,
  aes(
    x = term,
    y = estimate)) +
  geom_point() +
  geom_errorbar(
    aes(
      ymin = conf.low,
      ymax = conf.high),
    width = 0.2) +
  coord_flip() + # flip axes for readability
  labs(
    title = "Regression Coefficients with 95% CI",
    x = "Predictor",
    y = "Coefficient Estimate") +
  theme_minimal()
```

```{r}
#| label: fig-regressionCoefficientsStandardized
#| fig-cap: "Standardized Regression Coefficients with 95% Confidence Interval."
#| fig-alt: "Standardized Regression Coefficients with 95% Confidence Interval."

ggplot(
  quadraticTermsRegressionModelStandardized_tidy,
  aes(
    x = term,
    y = estimate)) +
  geom_point() +
  geom_errorbar(
    aes(
      ymin = conf.low,
      ymax = conf.high),
    width = 0.2) +
  coord_flip() + # flip axes for readability
  labs(
    title = "Regression Coefficients with 95% CI",
    x = "Predictor",
    y = "Standardized Coefficient Estimate") +
  theme_minimal()
```

#### Model-Implied Association {#sec-multipleRegressionVisualizingModelImpliedAssociation}

If we wanted to visualize the shape of the model-implied association between target share and fantasy points, we could generate the model-implied predictions using the data range that we want to visualize.
